Backscatter Modulation Design for Symbiotic Radio Networks

### 2021-12-15 main.tex
:pencil: Add optimality conditions of input distribution

				I_{\mathrm{B}}(\bar{c}_{m_{\mathcal{K}}} ; z) \triangleq \sum_j P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}}) \log \frac{P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}})}{P(\bar{z}_j)},

@@

			% 	I_{\mathrm{B}}(\bar{c}_{m_{\mathcal{K}}} ; z)

@@

			the backscatter marginal information function of tag $k$ associated with $\bar{c}_{m_{k}}$ is defined as

@@

				I_{\mathrm{B},k}(\bar{c}_{m_{k}} ; z) \triangleq \sum_{m_{\mathcal{K} \setminus \{k\}}} \prod_{k' \in \mathcal{K} \setminus \{k\}} P_{k'}(\bar{c}_{m_{k'}}) I_{\mathrm{B}}(\bar{c}_{m_{\mathcal{K}}} ; z),

@@

@@

			% 	I_{\mathrm{B},k}(\bar{c}_{m_{k}} ; z)
			% 	& \triangleq \sum_{m_{\mathcal{K} \setminus \{k\}}} P_{\mathcal{K} \setminus \{k\}}(\bar{c}_{m_{\mathcal{K} \setminus \{k\}}}) I_{\mathrm{B}}(\bar{c}_{m_{\mathcal{K}}} ; z)\\
			% 	& = \sum_{m_{\mathcal{K} \setminus \{k\}}} \prod_{k' \in \mathcal{K} \setminus \{k\}} P_{k'}(\bar{c}_{m_{k'}}) I_{\mathrm{B}}(\bar{c}_{m_{\mathcal{K}}} ; z),

@@

			% 	I_{\mathrm{B},\mathcal{S}}(\bar{c}_{m_{\mathcal{S}}} ; z) \triangleq \sum_{m_{\mathcal{K} \setminus \mathcal{S}}} P_{\mathcal{K} \setminus \mathcal{S}}(\bar{c}_{m_{\mathcal{K} \setminus \mathcal{S}}}) I_{\mathrm{B}}(\bar{c}_{m_{\mathcal{K}}} ; z),

@@

			and the backscatter mutual information can be expressed as\footnote{Please be aware that $c_{\mathcal{K}}$, $c_{\mathcal{S}}$, $z$ are random variables, while $\bar{c}_{m_{\mathcal{K}}}$ and $\bar{c}_i$, $\bar{c}_{m_{\mathcal{S}}}$, $\bar{z}_j$ represent the corresponding instances.}

@@

				I_{\mathrm{B}}(c_{\mathcal{K}} ; z)
				& = \mathbb{E}_{c_{\mathcal{K}}} \left[I_{\mathrm{B}}(\bar{c}_{m_{\mathcal{K}}} ; z)\right] = \mathbb{E}_{c_{k}} \left[I_{\mathrm{B},k}(\bar{c}_{m_{k}} ; z)\right]\\
				& = \sum_{m_{\mathcal{K}}} \prod_{k \in \mathcal{K}} P_k(\bar{c}_{m_k}) \sum_j P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}}) \log \frac{P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}})}{P(\bar{z}_j)}.\label{eq:backscatter_sum_rate}

@@

@@

			% 	I_{\mathrm{B}}(c_{\mathcal{K}} ; z)
			% 	& = \mathbb{E}_{c_{\mathcal{K}}} \left[I_{\mathrm{B}}(\bar{c}_{m_{\mathcal{K}}} ; z)\right] = \mathbb{E}_{c_{\mathcal{S}}} \left[I_{\mathrm{B},\mathcal{S}}(\bar{c}_{m_{\mathcal{S}}} ; z)\right]\\

@@

		\begin{subsection}{Ergodic primary rate}
			Once the tag input combination is successfully decoded, the user can eliminate backscatter uncertainty and model its contribution within the equivalent primary channel \eqref{eq:equivalent_primary_channel}. As such, the tags can adjust the propagation environment in a potentially beneficial manner, and create artificial channel variation within each fading block. Similarly, we define the primary information function associated with tag input combination $\bar{c}_{m_{\mathcal{K}}}$ and the primary marginal information function of tag $k$ associated with symbol $\bar{c}_{m_{k}}$ respectively as
			\begin{equation}
				I_{\mathrm{P}}(\bar{c}_{m_{\mathcal{K}}} ; \boldsymbol{y}) \triangleq N \log_2 \left(1 + \frac{\lvert \boldsymbol{h}_{\mathrm{E}}^H(\bar{c}_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_w^2}\right),
				\label{eq:primary_information_function}
			\end{equation}
			\begin{equation}
				I_{\mathrm{P},k}(\bar{c}_{m_{k}} ; \boldsymbol{y}) \triangleq \sum_{m_{\mathcal{K} \setminus \{k\}}} \prod_{k' \in \mathcal{K} \setminus \{k\}} P_{k'}(\bar{c}_{m_{k'}}) I_{\mathrm{P}}(\bar{c}_{m_{\mathcal{K}}} ; \boldsymbol{y}),
				\label{eq:primary_marginal_information_function}
			\end{equation}
			% \begin{equation}
			% 	I_{\mathrm{P},k}(\bar{c}_{m_{k}}) \triangleq \sum_{m_{\mathcal{K} \setminus \{k\}}} P_{\mathcal{K} \setminus \{k\}}(\bar{c}_{m_{\mathcal{K} \setminus \{k\}}}) I_{\mathrm{P}}(\bar{c}_{m_{\mathcal{K}}}),
			% 	\label{eq:primary_marginal_information_function}
			% \end{equation}
			% \begin{equation}
			% 	I_{\mathrm{P},\mathcal{S}}(\bar{c}_{m_{\mathcal{S}}}) \triangleq \sum_{m_{\mathcal{K} \setminus \mathcal{S}}} P_{\mathcal{K} \setminus \mathcal{S}}(\bar{c}_{m_{\mathcal{K} \setminus \mathcal{S}}}) I_{\mathrm{P}}(\bar{c}_{m_{\mathcal{K}}}),
			% 	\label{eq:primary_marginal_information_function}
			% \end{equation}
			and the ergodic primary rate can be expressed as \footnote{The unit of \eqref{eq:backscatter_information_function}, \eqref{eq:backscatter_marginal_information_function} and \eqref{eq:backscatter_sum_rate} are \gls{bpcu}, while the unit of \eqref{eq:primary_information_function}, \eqref{eq:primary_marginal_information_function} and \eqref{eq:primary_ergodic_rate} are \gls{bpsphz}.}
			\begin{align}
				I_{\mathrm{P}}(c_{\mathcal{K}} ; \boldsymbol{y})
				& = \mathbb{E}_{c_{\mathcal{K}}} \left[I_{\mathrm{P}}(\bar{c}_{m_{\mathcal{K}}} ; \boldsymbol{y})\right] = \mathbb{E}_{c_{k}} \left[I_{\mathrm{P},k}(\bar{c}_{m_{k}} ; \boldsymbol{y})\right]\\
				& = \sum_{m_{\mathcal{K}}} \prod_{k \in \mathcal{K}} P_k(\bar{c}_{m_k}) N \log_2 \left(1 + \frac{\lvert \boldsymbol{h}_{\mathrm{E}}^H(\bar{c}_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_w^2}\right).
				\label{eq:primary_ergodic_rate}
			\end{align}
			% \begin{align}
			% 	I_{\mathrm{P}}(c_{\mathcal{K}})
			% 	& = \mathbb{E}_{c_{\mathcal{K}}} \left[I_{\mathrm{P}}(\bar{c}_{m_{\mathcal{K}}})\right] = \mathbb{E}_{c_{\mathcal{S}}} \left[I_{\mathrm{P},\mathcal{S}}(\bar{c}_{m_{\mathcal{S}}})\right]\\
			% 	& = \sum_{m_{\mathcal{K}}} \prod_{k \in \mathcal{K}} P_k(\bar{c}_{m_k}) \log_2 \left(1 + \frac{\lvert \boldsymbol{h}_{\mathrm{E}}^H(\bar{c}_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_w^2}\right).
			% 	\label{eq:primary_ergodic_rate}
			% \end{align}

@@

	\begin{section}{Input Distribution, Decision Region, and Precoder Design}
		\begin{subsection}{Primary-backscatter rate region}
			First, we define the weighted sum marginal information of tag $k$ associated with symbol $\bar{c}_{m_{k}}$ and the weighted sum primary-backscatter rate respectively as
			\begin{align}
				I_{q}(\bar{c}_{m_{k}} ; \boldsymbol{y},z)
				& \triangleq \rho I_{\mathrm{P},q}(\bar{c}_{m_{k}} ; \boldsymbol{y}) + (1 - \rho) I_{\mathrm{B},q}(\bar{c}_{m_{k}} ; z),\\
				I(c_{\mathcal{K}} ; \boldsymbol{y}, z)
				& \triangleq \rho I_{\mathrm{P}}(c_{\mathcal{K}} ; \boldsymbol{y}) + (1 - \rho) I_{\mathrm{B}}(c_{\mathcal{K}} ; z)
			\end{align}
			where $\rho \in [0,1]$ denotes the priority of the primary link. To investigate how the primary and backscatter links influence each other, we optimize the input probability distribution, decision region, and transmit precoder to maximize the weighted sum rate subject to the average transmit power and input probability constraints

			\begin{maxi!}
				{\scriptstyle{\boldsymbol{P},\boldsymbol{t},\boldsymbol{w}}}{I}{\label{op:rate_region}}{\label{ob:weighted_sum_rate}}
				\addConstraint{\sum \nolimits_{m_k} P_k(\bar{c}_{m_k})}{=1,\quad\label{co:sum_probability}}{\forall k \in \mathcal{K}}
				\addConstraint{P_k(\bar{c}_{m_k})}{\ge 0,\quad\label{co:nonnegative_probability}}{\forall m_k \in \mathcal{M}, \ \forall k \in \mathcal{K}}
				\addConstraint{\lVert \boldsymbol{w} \rVert^2}{\le P.\label{co:average_transmit_power}}
			\end{maxi!}

			As problem \eqref{op:rate_region} is not jointly convex over $\boldsymbol{P}$, $\boldsymbol{t}$ and $\boldsymbol{w}$, we propose a \gls{bcd} method that iteratively updates the input distribution, decision region, and transmit precoder, until convergence is achieved.
		\end{subsection}

		\begin{subsection}{Input probability distribution}
			For any fixed decision boundary $\boldsymbol{t}$ and transmit precoder $\boldsymbol{w}$, the equivalent discrete memoryless \gls{mac} can be determined by \eqref{eq:mac} and problem~\eqref{op:rate_region} boils down to
			\begin{maxi!}
				{\scriptstyle{\boldsymbol{P}}}{I}{\label{op:input_probability_distribution}}{}
				\addConstraint{\eqref{co:sum_probability},\eqref{co:nonnegative_probability},}
			\end{maxi!}
			which is non-convex for $K > 1$ due to the product term $\prod_{k \in \mathcal{K}} P_k(\bar{c}_{m_k})$. Fortunately, the \gls{kkt} conditions are sufficient and necessary for this type of problem, and the proof follows straightforwardly from \cite{Watanabe2009}.\footnote{For any elementary discrete memoryless \gls{mac} (sizes of input alphabets are no greater than that of output alphabet), the sufficiency can be proved by combining the local maximum and connectedness of \gls{kkt} solutions. For any general discrete memoryless \gls{mac}, the capacity can be achieved by an elementary discrete memoryless \gls{mac} included within. Thus, we restrict the discussion of this paper to elementary discrete memoryless \gls{mac}s.} Denote the Lagrange multiplier associated with \eqref{co:sum_probability} and \eqref{co:nonnegative_probability} as $\boldsymbol{\mu} \triangleq [\mu_1,\ldots,\mu_K]^T \in \mathbb{R}^{K \times 1}$ and $\boldsymbol{\Lambda} \triangleq [\boldsymbol{\lambda}_1^T,\ldots,\boldsymbol{\lambda}_K^T]^T \in \mathbb{R}^{M \times K}$ with $\boldsymbol{\lambda}_k \triangleq [\lambda_{k,1},\ldots,\lambda_{k,M}]^T \in \mathbb{R}^{M \times 1}$, respectively. The Lagrangian function of problem~\eqref{op:input_probability_distribution} is
			\begin{align}
				J
				& = - I + \sum_{k \in \mathcal{K}} \mu_k \left( \sum_{m_k \in \mathcal{M}} P_k(\bar{c}_{m_k}) - 1 \right)\nonumber\\
				& \quad - \sum_{k \in \mathcal{K}} \sum_{m_k \in \mathcal{M}} \lambda_{k,m_k} P_k(\bar{c}_{m_k}),
			\end{align}
			and the corresponding \gls{kkt} conditions on the primal and dual solutions are, $\forall i_q \in \mathcal{M}$ and $\forall q \in \mathcal{K}$,
			\begin{subequations}
				\begin{equation}
					- \pdv{I}{P_q^{\star}(\bar{c}_{i_q})} + \mu_q^{\star} - \lambda_{q,i_q}^{\star} = 0,
				\end{equation}
				\begin{equation}
					\lambda_{q,i_q}^{\star} = 0, \quad P_q^{\star}(\bar{c}_{i_q}) > 0,
				\end{equation}
				\begin{equation}
					\lambda_{q,i_q}^{\star} \ge 0, \quad P_q^{\star}(\bar{c}_{i_q}) = 0,
				\end{equation}
			\end{subequations}
			and the partial derivative can be explicitly expressed as
			% \begin{equation}
			% 	\pdv{I}{P_q^{\star}(\bar{c}_{i_q})} = \rho I_{\mathrm{P},q}(\bar{c}_{i_q} ; \boldsymbol{y}) + (1 - \rho) \left( I_{\mathrm{B},q}(\bar{c}_{i_q} ; z) - 1 \right).
			% \end{equation}
			\begin{align}
				\pdv{I}{P_q^{\star}(\bar{c}_{i_q})}
				& = \rho I_{\mathrm{P},q}(\bar{c}_{i_q} ; \boldsymbol{y}) + (1 - \rho) \left( I_{\mathrm{B},q}(\bar{c}_{i_q} ; z) - 1 \right)\\
				& = I_{q}(\bar{c}_{i_q} ; \boldsymbol{y},z) - (1 - \rho).
			\end{align}
			which suggests $\mu_q^{\star}$ must satisfy
			\begin{subequations}
				\begin{equation}
					\mu_q^{\star} = I_{q}(\bar{c}_{i_q} ; \boldsymbol{y},z) - (1 - \rho), \quad P_q^{\star}(\bar{c}_{i_q}) > 0,
				\end{equation}
				\begin{equation}
					\mu_q^{\star} \ge I_{q}(\bar{c}_{i_q} ; \boldsymbol{y},z) - (1 - \rho), \quad P_q^{\star}(\bar{c}_{i_q}) = 0.
				\end{equation}
			\end{subequations}

			Due to the sufficiency and necessity of the \gls{kkt} conditions, we can conclude that any input probability distribution $\boldsymbol{P}^{\star}$ maximizes the weighted sum primary-backscatter rate if and only if, $\forall i_q \in \mathcal{M}$ and $\forall q \in \mathcal{K}$,
			\begin{subequations}
				\begin{equation}
					I_{q}(\bar{c}_{i_q} ; \boldsymbol{y},z) = C_q, \quad P_q^{\star}(\bar{c}_{i_q}) > 0,
				\end{equation}
				\begin{equation}
					I_{q}(\bar{c}_{i_q} ; \boldsymbol{y},z) \le C_q, \quad P_q^{\star}(\bar{c}_{i_q}) = 0,
				\end{equation}
			\end{subequations}
		\end{subsection}

>>>>

				I_{\mathrm{B}}(\bar{c}_{m_{\mathcal{K}}};z) \triangleq \sum_j P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}}) \log \frac{P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}})}{P(\bar{z}_j)},

@@

			% 	I_{\mathrm{B}}(\bar{c}_{m_{\mathcal{K}}};z)

@@

			the backscatter marginal information function of tag $q \in \mathcal{K}$ associated with $\bar{c}_{i_q}$, $i_q \in \mathcal{M}$ is defined as

@@

				I_{\mathrm{B},q}(\bar{c}_{i_q};z) \triangleq \sum_{m_{\mathcal{K} \setminus \{q\}}} \prod_{k \in \mathcal{K} \setminus \{q\}} P_k(\bar{c}_{m_k}) I_{\mathrm{B}}(\bar{c}_{m_{\mathcal{K} \setminus \{q\}}},\bar{c}_{i_q};z),

@@

			% the backscatter marginal information function of tag $k$ associated with $\bar{c}_{m_k}$ is defined as
			% 	I_{\mathrm{B},k}(\bar{c}_{m_k};z) \triangleq \sum_{m_{\mathcal{K} \setminus \{k\}}} \prod_{k' \in \mathcal{K} \setminus \{k\}} P_{k'}(\bar{c}_{m_{k'}}) I_{\mathrm{B}}(\bar{c}_{m_{\mathcal{K} \setminus \{k\}}}, \bar{c}_{m_k};z),
			% 	% \label{eq:backscatter_marginal_information_function}
			% 	I_{\mathrm{B},k}(\bar{c}_{m_k};z) \triangleq \sum_{m_{\mathcal{K} \setminus \{k\}}} \prod_{k' \in \mathcal{K} \setminus \{k\}} P_{k'}(\bar{c}_{m_{k'}}) I_{\mathrm{B}}(\bar{c}_{m_{\mathcal{K}}};z),

@@

			% 	I_{\mathrm{B},k}(\bar{c}_{m_k};z)
			% 	& \triangleq \sum_{m_{\mathcal{K} \setminus \{k\}}} P_{\mathcal{K} \setminus \{k\}}(\bar{c}_{m_{\mathcal{K} \setminus \{k\}}}) I_{\mathrm{B}}(\bar{c}_{m_{\mathcal{K}}};z)\\
			% 	& = \sum_{m_{\mathcal{K} \setminus \{k\}}} \prod_{k' \in \mathcal{K} \setminus \{k\}} P_{k'}(\bar{c}_{m_{k'}}) I_{\mathrm{B}}(\bar{c}_{m_{\mathcal{K}}};z),
			% 	% \label{eq:backscatter_marginal_information_function}

@@

			% 	I_{\mathrm{B},\mathcal{S}}(\bar{c}_{m_{\mathcal{S}}};z) \triangleq \sum_{m_{\mathcal{K} \setminus \mathcal{S}}} P_{\mathcal{K} \setminus \mathcal{S}}(\bar{c}_{m_{\mathcal{K} \setminus \mathcal{S}}}) I_{\mathrm{B}}(\bar{c}_{m_{\mathcal{K}}};z),

@@

			and the backscatter mutual information can be expressed as\footnote{Please be aware that $c_{\mathcal{K}}$, $c_k$, $z$ are random variables, while $\bar{c}_{m_{\mathcal{K}}}$ and $\bar{c}_i$, $\bar{c}_{m_k}$, $\bar{z}_j$ represent the corresponding instances.}
			\begin{subequations}

@@

					I_{\mathrm{B}}(c_{\mathcal{K}};z)
					& = \mathbb{E}_{c_{\mathcal{K}}} \left[I_{\mathrm{B}}(\bar{c}_{m_{\mathcal{K}}};z)\right] = \mathbb{E}_{c_k} \left[I_{\mathrm{B},k}(\bar{c}_{m_k};z)\right]\label{eq:backscatter_sum_rate_expectation}\\
					& = \sum_{m_{\mathcal{K}}} \prod_{k \in \mathcal{K}} P_k(\bar{c}_{m_k}) \sum_j P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}}) \log \frac{P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}})}{P(\bar{z}_j)}.\label{eq:backscatter_sum_rate_expansion}

@@

				\label{eq:backscatter_sum_rate}
			\end{subequations}

@@

			% 	I_{\mathrm{B}}(c_{\mathcal{K}};z)
			% 	& = \mathbb{E}_{c_{\mathcal{K}}} \left[I_{\mathrm{B}}(\bar{c}_{m_{\mathcal{K}}};z)\right] = \mathbb{E}_{c_{\mathcal{S}}} \left[I_{\mathrm{B},\mathcal{S}}(\bar{c}_{m_{\mathcal{S}}};z)\right]\\

@@

		\begin{subsection}{Ergodic primary rate}
			Once the tag input combination is successfully decoded, the user can eliminate backscatter uncertainty and model its contribution within the equivalent primary channel \eqref{eq:equivalent_primary_channel}. As such, the tags can adjust the propagation environment in a potentially beneficial manner, and create artificial channel variation within each fading block. Similarly, we define the primary information function associated with tag input combination $\bar{c}_{m_{\mathcal{K}}}$ and the primary marginal information function of tag $q$ associated with symbol $\bar{c}_{i_q}$ respectively as
			\begin{align}
				I_{\mathrm{P}}(\bar{c}_{m_{\mathcal{K}}};\boldsymbol{y})
				& \triangleq N \log_2 \left(1 + \frac{\lvert \boldsymbol{h}_{\mathrm{E}}^H(\bar{c}_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_w^2}\right),\label{eq:primary_information_function}\\
				I_{\mathrm{P},q}(\bar{c}_{i_q};\boldsymbol{y})
				& \triangleq \sum_{m_{\mathcal{K} \setminus \{q\}}} \prod_{k \in \mathcal{K} \setminus \{q\}} P_{k}(\bar{c}_{m_{k}}) I_{\mathrm{P}}(\bar{c}_{m_{\mathcal{K} \setminus \{q\}}},\bar{c}_{i_q};\boldsymbol{y}),\label{eq:primary_marginal_information_function}
			\end{align}
			% \begin{equation}
			% 	I_{\mathrm{P},k}(\bar{c}_{m_k};\boldsymbol{y}) \triangleq \sum_{m_{\mathcal{K} \setminus \{k\}}} \prod_{k' \in \mathcal{K} \setminus \{k\}} P_{k'}(\bar{c}_{m_{k'}}) I_{\mathrm{P}}(\bar{c}_{m_{\mathcal{K}}};\boldsymbol{y}),
			% 	\label{eq:primary_marginal_information_function}
			% \end{equation}
			% \begin{equation}
			% 	I_{\mathrm{P},k}(\bar{c}_{m_k}) \triangleq \sum_{m_{\mathcal{K} \setminus \{k\}}} P_{\mathcal{K} \setminus \{k\}}(\bar{c}_{m_{\mathcal{K} \setminus \{k\}}}) I_{\mathrm{P}}(\bar{c}_{m_{\mathcal{K}}}),
			% 	\label{eq:primary_marginal_information_function}
			% \end{equation}
			% \begin{equation}
			% 	I_{\mathrm{P},\mathcal{S}}(\bar{c}_{m_{\mathcal{S}}}) \triangleq \sum_{m_{\mathcal{K} \setminus \mathcal{S}}} P_{\mathcal{K} \setminus \mathcal{S}}(\bar{c}_{m_{\mathcal{K} \setminus \mathcal{S}}}) I_{\mathrm{P}}(\bar{c}_{m_{\mathcal{K}}}),
			% 	\label{eq:primary_marginal_information_function}
			% \end{equation}
			and the ergodic primary rate can be expressed as\footnote{The unit of \eqref{eq:backscatter_information_function}--\eqref{eq:backscatter_sum_rate} are \gls{bpcu}, while the unit of \eqref{eq:primary_information_function}--\eqref{eq:primary_ergodic_rate} are \gls{bpsphz}.}
			\begin{subequations}
				\begin{align}
					I_{\mathrm{P}}(c_{\mathcal{K}};\boldsymbol{y})
					& = \mathbb{E}_{c_{\mathcal{K}}} \left[I_{\mathrm{P}}(\bar{c}_{m_{\mathcal{K}}};\boldsymbol{y})\right] = \mathbb{E}_{c_k} \left[I_{\mathrm{P},k}(\bar{c}_{m_k};\boldsymbol{y})\right]\label{eq:primary_ergodic_rate_expectation}\\
					& = \sum_{m_{\mathcal{K}}} \prod_{k \in \mathcal{K}} P_k(\bar{c}_{m_k}) N \log_2 \left(1 + \frac{\lvert \boldsymbol{h}_{\mathrm{E}}^H(\bar{c}_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_w^2}\right).
					\label{eq:primary_ergodic_rate_expansion}
				\end{align}
				\label{eq:primary_ergodic_rate}
			\end{subequations}
			% \begin{align}
			% 	I_{\mathrm{P}}(c_{\mathcal{K}})
			% 	& = \mathbb{E}_{c_{\mathcal{K}}} \left[I_{\mathrm{P}}(\bar{c}_{m_{\mathcal{K}}})\right] = \mathbb{E}_{c_{\mathcal{S}}} \left[I_{\mathrm{P},\mathcal{S}}(\bar{c}_{m_{\mathcal{S}}})\right]\\
			% 	& = \sum_{m_{\mathcal{K}}} \prod_{k \in \mathcal{K}} P_k(\bar{c}_{m_k}) \log_2 \left(1 + \frac{\lvert \boldsymbol{h}_{\mathrm{E}}^H(\bar{c}_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_w^2}\right).
			% 	\label{eq:primary_ergodic_rate}
			% \end{align}

@@

	\begin{section}{Input Distribution, Decision Region, and Precoder Design}
		\begin{subsection}{Primary-backscatter rate region}
			The weighted sum marginal information of tag $q$ associated with symbol $\bar{c}_{i_q}$ and the weighted sum primary-backscatter rate are defined respectively as
			\begin{align}
				I_q(\bar{c}_{i_q};\boldsymbol{y},z)
				& \triangleq \rho I_{\mathrm{P},q}(\bar{c}_{i_q};\boldsymbol{y}) + (1 - \rho) I_{\mathrm{B},q}(\bar{c}_{i_q};z),\label{eq:weighted_sum_marginal_information}\\
				I(c_{\mathcal{K}};\boldsymbol{y},z)
				& \triangleq \rho I_{\mathrm{P}}(c_{\mathcal{K}};\boldsymbol{y}) + (1 - \rho) I_{\mathrm{B}}(c_{\mathcal{K}};z),\label{eq:weighted_sum_rate}
			\end{align}
			where $\rho \in [0,1]$ denotes the priority of the primary link. To investigate how backscatter modulation and detection may influence the primary transmission, we optimize the input probability distribution, decision region, and transmit precoder to maximize the weighted primary-backscatter sum rate
			\begin{maxi!}
				{\scriptstyle{\boldsymbol{P},\boldsymbol{t},\boldsymbol{w}}}{I}{\label{op:rate_region}}{\label{ob:weighted_sum_rate}}
				\addConstraint{\sum \nolimits_{m_k} P_k(\bar{c}_{m_k})}{=1,\quad\label{co:sum_probability}}{\forall k \in \mathcal{K}}
				\addConstraint{P_k(\bar{c}_{m_k})}{\ge 0,\quad\label{co:nonnegative_probability}}{\forall m_k \in \mathcal{M}, \ \forall k \in \mathcal{K}}
				\addConstraint{\lVert \boldsymbol{w} \rVert^2}{\le P.\label{co:average_transmit_power}}
			\end{maxi!}
			where \eqref{co:sum_probability} and \eqref{co:nonnegative_probability} are input probability constraints and \eqref{co:average_transmit_power} is the average transmit power budget. As problem \eqref{op:rate_region} is not jointly convex over $\boldsymbol{P}$, $\boldsymbol{t}$ and $\boldsymbol{w}$, we propose a \gls{bcd} method that iteratively updates the input distribution, decision region, and transmit precoder, until convergence is achieved.
		\end{subsection}

		\begin{subsection}{Input probability distribution}
			For any fixed decision boundary $\boldsymbol{t}$ and transmit precoder $\boldsymbol{w}$, the equivalent discrete memoryless \gls{mac} can be determined by \eqref{eq:mac} and problem~\eqref{op:rate_region} boils down to
			\begin{maxi!}
				{\scriptstyle{\boldsymbol{P}}}{I}{\label{op:input_probability_distribution}}{}
				\addConstraint{\eqref{co:sum_probability},\eqref{co:nonnegative_probability},}
			\end{maxi!}
			which is non-convex for $K > 1$ due to the product term $\prod_{k \in \mathcal{K}} P_k(\bar{c}_{m_k})$. Fortunately, the \gls{kkt} conditions are sufficient and necessary for this type of problem, and the proof follows straightforwardly from \cite{Watanabe2009}.\footnote{For any elementary discrete memoryless \gls{mac} (sizes of input alphabets are no greater than that of output alphabet), the sufficiency can be proved by combining the local maximum and connectedness of \gls{kkt} solutions. For any general discrete memoryless \gls{mac}, the capacity can be achieved by an elementary discrete memoryless \gls{mac} included within. Thus, we restrict the discussion of this paper to elementary discrete memoryless \gls{mac}s.} Denote the Lagrange multiplier associated with \eqref{co:sum_probability} and \eqref{co:nonnegative_probability} as $\boldsymbol{\mu} \triangleq [\mu_1,\ldots,\mu_K]^T \in \mathbb{R}^{K \times 1}$ and $\boldsymbol{\Lambda} \triangleq [\boldsymbol{\lambda}_1^T,\ldots,\boldsymbol{\lambda}_K^T]^T \in \mathbb{R}^{M \times K}$ with $\boldsymbol{\lambda}_k \triangleq [\lambda_{k,1},\ldots,\lambda_{k,M}]^T \in \mathbb{R}^{M \times 1}$, respectively. The Lagrangian function of problem~\eqref{op:input_probability_distribution} is
			\begin{align}
				J
				& = - I + \sum_{k \in \mathcal{K}} \mu_k \left( \sum_{m_k \in \mathcal{M}} P_k(\bar{c}_{m_k}) - 1 \right)\nonumber\\
				& \quad - \sum_{k \in \mathcal{K}} \sum_{m_k \in \mathcal{M}} \lambda_{k,m_k} P_k(\bar{c}_{m_k}),
			\end{align}
			and the corresponding \gls{kkt} conditions on the primal and dual solutions are, $\forall i_q \in \mathcal{M}$ and $\forall q \in \mathcal{K}$,
			\begin{subequations}
				\begin{equation}
					- \pdv{I}{P_q^{\star}(\bar{c}_{i_q})} + \mu_q^{\star} - \lambda_{q,i_q}^{\star} = 0,
				\end{equation}
				\begin{equation}
					\lambda_{q,i_q}^{\star} = 0, \quad P_q^{\star}(\bar{c}_{i_q}) > 0,
				\end{equation}
				\begin{equation}
					\lambda_{q,i_q}^{\star} \ge 0, \quad P_q^{\star}(\bar{c}_{i_q}) = 0.
				\end{equation}
			\end{subequations}

			The partial derivative can be explicitly expressed as
			\begin{subequations}
				\begin{align}
					\pdv{I}{P_q^{\star}(\bar{c}_{i_q})}
					& = \rho I_{\mathrm{P},q}(\bar{c}_{i_q};\boldsymbol{y}) + (1 - \rho) \left( I_{\mathrm{B},q}(\bar{c}_{i_q};z) - 1 \right)\\
					& = I_q(\bar{c}_{i_q};\boldsymbol{y},z) - (1 - \rho),
				\end{align}
			\end{subequations}
			which suggests $\mu_q^{\star}$ must satisfy
			\begin{subequations}
				\begin{alignat}{2}
					\mu_q^{\star} & = I_q(\bar{c}_{i_q};\boldsymbol{y},z) - (1 - \rho), \quad && P_q^{\star}(\bar{c}_{i_q}) > 0,\\
					\mu_q^{\star} & \ge I_q(\bar{c}_{i_q};\boldsymbol{y},z) - (1 - \rho), \quad && P_q^{\star}(\bar{c}_{i_q}) = 0.
				\end{alignat}
			\end{subequations}

			Due to the sufficiency and necessity of the \gls{kkt} conditions, we can conclude that any input probability distribution $\boldsymbol{P}^{\star}$ maximizes the weighted sum primary-backscatter rate if and only if, $\forall i_q \in \mathcal{M}$ and $\forall q \in \mathcal{K}$,
			\begin{subequations}
				\begin{alignat}{2}
					I_q(\bar{c}_{i_q};\boldsymbol{y},z) & = C_q, \quad && P_q^{\star}(\bar{c}_{i_q}) > 0,\\
					I_q(\bar{c}_{i_q};\boldsymbol{y},z) & \le C_q, \quad && P_q^{\star}(\bar{c}_{i_q}) = 0,
				\end{alignat}
			\end{subequations}
			where $C_q \triangleq \mu_q^{\star} + (1 - \rho)$. Apparently, it holds that
			\begin{equation}
				\sum_{i_q} P_q^{\star}(\bar{c}_{i_q}) I_q(\bar{c}_{i_q};\boldsymbol{y},z) = C_q.
			\end{equation}

			On the other hand, by the definition of marginations \eqref{eq:backscatter_sum_rate_expectation}, \eqref{eq:primary_ergodic_rate_expectation} and weighted summations \eqref{eq:weighted_sum_marginal_information}, \eqref{eq:weighted_sum_rate}, we have
			\begin{equation}
				\sum_{i_q} P_q^{\star}(\bar{c}_{i_q}) I_q(\bar{c}_{i_q};\boldsymbol{y},z) = I(c_{\mathcal{K}};\boldsymbol{y},z),
			\end{equation}
			which is irrelevant to $q$. Hence, $C_q = I(c_{\mathcal{K}};\boldsymbol{y},z)$, $\forall q \in \mathcal{K}$ and
			\begin{subequations}
				\begin{alignat}{2}
					I_q(\bar{c}_{i_q};\boldsymbol{y},z) & = I(c_{\mathcal{K}};\boldsymbol{y},z), \quad && P_q^{\star}(\bar{c}_{i_q}) > 0,\\
					I_q(\bar{c}_{i_q};\boldsymbol{y},z) & \le I(c_{\mathcal{K}};\boldsymbol{y},z), \quad && P_q^{\star}(\bar{c}_{i_q}) = 0.
				\end{alignat}
			\end{subequations}

			It suggests that an input probability distribution maximizes the weighted primary-backscatter sum rate if and only if each probable state of each tag produces the same mutual information.
		\end{subsection}
